\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-04 paper/draft.tex
Comments and improvements in abstract

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\fixme}[1]{{\color{red}#1}}
\newcommand{\nv}[1]{[{\color{cyan}nv: #1}]}
\newcommand{\kk}[1]{[{\color{magenta}kk: #1}]}
\newcommand{\km}[1]{[{\color{blue}km: #1}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system aimed at parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
% a source-to-source shell compiler and associated runtime library
Given a script, \sys converts it to a data-flow graph, performs a series of analyses that aim at exposing parallelism while preserving its sequential semantics, and then converts the data-flow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
A set of lightweight annotations allow command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands, two large and commonly used groups, 
informs \sys's annotation language and results in its equivalent of a data-parallel standard library.
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation, combining several classic and modern Unix scripts, shows significant benefits across several axes---with order-of-magnitude performance improvements stemming from the combination of its program transformations and runtime primitives.
\end{abstract}

@@

\heading{Example Annotations}
The parallelizability properties of each command are written in an annotation record that
%% An annotation record
contains a set of clauses, each one identified by a predicate on the command options.
Each clause maps to an assignment for the command, indicating its class and the sequence of its inputs and outputs.
Annotations treat flag arguments differently from file arguments, by checking if they start with a \ttt{-}.
% \footnote{
%   Note that the single character \ttt{-} is not an option as it is most often used to designate that a command reads from its standard input.
%   \nv{
%     There are options of of the form --f "x; y", and BSD options do not take \ttt{-} (like \ttt{ps aux}).
%     I am also not sure how important this last sentence is, as it did not answer a question I had---I expected arguments to be anything: if soneome wants to put ``pizza'' the DSL should not disallow it.
%   }
% }
The complete annotation grammar is shown in Appendix~\ref{alg}.

For example, consider \ttt{comm}, which performs a join-like operation on its two inputs to identify common elements.
When \ttt{comm} is invoked without any flags, it produces a three-column output:
  the first column contains lines that are unique to the first input, the second column contains lines that are unique to the second input, and the last column contains lines that exist in both inputs.
A user can invoke \ttt{comm} with any combination of flags \ttt{-1}, \ttt{-2}, or \ttt{-3} to suppress the corresponding output column(s).
Its annotation record is shown below:
%
\begin{lstlisting}[language=sh, numbers=none]
comm {
| -1 /\ -3 => (S, [arg[1]], [stdout])
| -2 /\ -3 => (S, [arg[0]], [stdout])
| _  => (P, [arg[0], arg[1]], [stdout])
}
\end{lstlisting}

>>>>

% For comments
\newcommand{\eat}[1]{}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\fixme}[1]{{\color{red}#1}}
\newcommand{\nv}[1]{[{\color{cyan}nv: #1}]}
\newcommand{\kk}[1]{[{\color{magenta}kk: #1}]}
\newcommand{\km}[1]{[{\color{blue}km: #1}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\tr}[1]{} %% Text and comments for technical report
\newcommand{\str}{{\color{red}\textbf{\ttt{*}}}}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
This paper presents \sys, a system aimed at parallelizing POSIX shell scripts through a combination of program transformations and runtime primitives.
% a source-to-source shell compiler and associated runtime library
Given a script, \sys converts it to a data-flow graph, performs a series of analyses that aim at exposing parallelism while preserving its sequential semantics, and then converts the data-flow graph back into a script that uses POSIX constructs to explicitly guide parallelism.
%% \kk{Sys converts a script into several data-flow graphs. Does precision matter here? Should we be super explicit about what it does?}
A lightweight annotation language allow command developers to express key parallelizability properties about their commands.
An accompanying parallelizability study of POSIX and GNU commands, two large and commonly used groups, 
informs \sys's annotation language and guides the development of a data-parallel standard library.
% \kk{Can we extend this to say that PaSh automatically uses constructs from this library? Otherwise it sounds like the user has to use it to make their scripts parallel.}
Finally, \sys's \unix-aware runtime primitives address several practical issues related to performance and correctness.
\sys's extensive evaluation, combining several classic and modern Unix scripts, shows significant benefits across several axes---with order-of-magnitude performance improvements stemming from the combination of its program transformations and runtime primitives.
% \kk{What are the several axes? We only show speedup. I would propose renaming to significant benefits in execution time.}
\end{abstract}

@@

\heading{Example Annotations}
The parallelizability properties of each command are written in an annotation record that
%% An annotation record
contains a set of clauses, each one identified by a predicate on the command options.
Each clause maps to an assignment for the command, indicating its class and the sequence of its inputs and outputs.
Annotations treat flag arguments differently from file arguments, by checking if they start with a \ttt{-}.
% \footnote{
%   Note that the single character \ttt{-} is not an option as it is most often used to designate that a command reads from its standard input.
%   \nv{
%     There are options of of the form --f "x; y", and BSD options do not take \ttt{-} (like \ttt{ps aux}).
%     I am also not sure how important this last sentence is, as it did not answer a question I had---I expected arguments to be anything: if soneome wants to put ``pizza'' the DSL should not disallow it.
%   }
% }
The complete annotation grammar is shown in Appendix~\ref{alg}. \str
% \kk{EuroSys doesn't allow appendix. I think we should just remove the grammar.}
% \kk{We should mention somewhere that we used the language to annotate N commands.} 
% \kk{Mention that some commands, such as xargs are handled internally due to their particularities.}

For example, consider \ttt{comm}, which performs a join-like operation on its two inputs to identify common elements.
When \ttt{comm} is invoked without any flags, it produces a three-column output:
  the first column contains lines that are unique to the first input, the second column contains lines that are unique to the second input, and the last column contains lines that exist in both inputs.
A user can invoke \ttt{comm} with any combination of flags \ttt{-1}, \ttt{-2}, or \ttt{-3} to suppress the corresponding output column(s).
Its annotation record is shown below:\str
% \kk{Update with an excerpt from `comm`.}
%
\begin{lstlisting}[language=sh, numbers=none]
comm {
| -1 /\ -3 => (S, [arg[1]], [stdout])
| -2 /\ -3 => (S, [arg[0]], [stdout])
| _  => (P, [arg[0], arg[1]], [stdout])
}
\end{lstlisting}
